Casting doubt on the causal link between intelligence and age at first intercourse:\\ A cross-generational sibling comparison design using the NLSY

### 2016-09-24 Manuscript/Manuscript.Rnw
update

\documentclass[a4paper,man,apacite,natbib,12pt,longtable,mask]{apa6}
\usepackage{../Common/style/Mason}
\usepackage{listings}
\usepackage{inconsolata}
\usepackage[bottom]{footmisc} %fix footnotes
\usepackage{lineno}
\usepackage{adjustbox}
%\linenumbers
\interfootnotelinepenalty=10000
%%%%%%%%%%%% Title %%%%%%%%%%%%
\title{Casting doubt on the causal link between intelligence and age at first intercourse:\\ A cross-generational sibling comparison design using the NLSY}
\shorttitle{Intelligence and AFI}
%
% Authors and Affiliations
\author{S. Mason Garrison and Joseph Lee Rodgers}
\affiliation{Vanderbilt University}
%
% Author Note
\authornote{\input{../Common/content/title/authornote.tex}}
%
% Abstract
\abstract{%Last compiled \today\ at \currenttime\\
\input{../Common/content/title/abstract_empreport.txt}}
%
% Key Words
\keywords{Age at first intercourse; Cross-sectional Data; Discordant Sibling Design; Intelligence; Quasi-Experimental; Siblings}
%
\begin{document}
\maketitle

@@

  listing <- function(x, options){
    paste("\\begin{lstlisting}[style=Rsettings]\n",
      x, "\\end{lstlisting}\n", sep = "")}
  knit_hooks$set(source=listing, output=listing)
@
<<setup, include=FALSE>>=
# Libraries
## Install Most Current Version
library(devtools)#;dev_mode(on=T)
#install_github("LiveOak/NlsyLinks")
#install_github("harrelfe/Hmisc");dev_mode(on=F)
## Attach Remaining
library(corrplot)
library(ggplot2);library(ggExtra);library(gtable)
library(grid);library(gridExtra)
library(Hmisc)
library(MplusAutomation)
library(NlsyLinks)
library(plyr);library(psych)
library(QuantPsyc)
#library(stargazer)
library(tables)
library(xtable)

@@

#### Age 11
capture.output(stargazer(ModelSummaries_Mplusg2_11,summary=FALSE,flip = TRUE, dep.var.labels.include = FALSE),file=paste0(directory,"/Common/content/tables/table_g2_11measurement.tex"))
capture.output(stargazer(g2loading_11,summary=FALSE,flip = FALSE, dep.var.labels.include = FALSE),file=paste0(directory,"/Common/content/tables/table_g2loading_11.tex"))
@
<<results_regression,echo=FALSE, comment=NA, include=FALSE,cache=TRUE>>=
# Stargazer Plot defaults
font.size="small"
no.space=TRUE
style="demography"
column.sep.width = "1pt"
header = FALSE
column.labels = c("Mixed", "Daughters", "Sons")
model.numbers=FALSE
float=FALSE
ci =TRUE
single.row = TRUE
notes.append = TRUE
# 9.5
capture.output(stargazer(model.meanmoms_9,model.meanmoms.g_9,model.meanmoms.b_9,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Mom_Intelligence_Mean_Child_AFI_9.tex"))

capture.output(stargazer(model.meankids_9,model.meankids.g_9,model.meankids.b_9,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Child_Intelligence_Mean_Child_AFI_9.tex"))

capture.output(stargazer(model.meanmomskids_9,model.meanmomskids.g_9,model.meanmomskids.b_9,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel","Gen2 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Joint_Intelligence_Mean_Child_AFI_9.tex"))

capture.output(stargazer(model.diffmoms_9,model.diffmoms.g_9,model.diffmoms.b_9,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen1 Mean Intel", "Gen1 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Mom_Intelligence_Dif_Child_AFI_9.tex"))

capture.output(stargazer(model.diffkids_9,model.diffkids.g_9,model.diffkids.b_9,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen2 Mean Intel", "Gen2 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Child_Intelligence_Dif_Child_AFI_9.tex"))

capture.output(stargazer(model.diffmomskids_9,model.diffmomskids.g_9,model.diffmomskids.b_9,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen2 Mean Intel","Gen1 Mean Intel","Gen2 Dif Intel","Gen1 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Joint_Intelligence_Dif_Child_AFI_9.tex"))

# 10.5
capture.output(stargazer(model.meanmoms_10,model.meanmoms.g_10,model.meanmoms.b_10,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Mom_Intelligence_Mean_Child_AFI_10.tex"))

capture.output(stargazer(model.meankids_10,model.meankids.g_10,model.meankids.b_10,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Child_Intelligence_Mean_Child_AFI_10.tex"))

capture.output(stargazer(model.meanmomskids_10,model.meanmomskids.g_10,model.meanmomskids.b_10,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel","Gen2 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Joint_Intelligence_Mean_Child_AFI_10.tex"))

capture.output(stargazer(model.diffmoms_10,model.diffmoms.g_10,model.diffmoms.b_10,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen1 Mean Intel", "Gen1 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Mom_Intelligence_Dif_Child_AFI_10.tex"))

capture.output(stargazer(model.diffkids_10,model.diffkids.g_10,model.diffkids.b_10,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen2 Mean Intel", "Gen2 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Child_Intelligence_Dif_Child_AFI_10.tex"))

capture.output(stargazer(model.diffmomskids_10,model.diffmomskids.g_10,model.diffmomskids.b_10,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen2 Mean Intel","Gen1 Mean Intel","Gen2 Dif Intel","Gen1 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Joint_Intelligence_Dif_Child_AFI_10.tex"))

# 11.5
capture.output(stargazer(model.meanmoms_11,model.meanmoms.g_11,model.meanmoms.b_11,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Mom_Intelligence_Mean_Child_AFI_11.tex"))

capture.output(stargazer(model.meankids_11,model.meankids.g_11,model.meankids.b_11,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Child_Intelligence_Mean_Child_AFI_11.tex"))

capture.output(stargazer(model.meanmomskids_11,model.meanmomskids.g_11,model.meanmomskids.b_11,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel","Gen2 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Joint_Intelligence_Mean_Child_AFI_11.tex"))

capture.output(stargazer(model.diffmoms_11,model.diffmoms.g_11,model.diffmoms.b_11,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen1 Mean Intel", "Gen1 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Mom_Intelligence_Dif_Child_AFI_11.tex"))

capture.output(stargazer(model.diffkids_11,model.diffkids.g_11,model.diffkids.b_11,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen2 Mean Intel", "Gen2 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Child_Intelligence_Dif_Child_AFI_11.tex"))

capture.output(stargazer(model.diffmomskids_11,model.diffmomskids.g_11,model.diffmomskids.b_11,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen2 Mean Intel","Gen1 Mean Intel","Gen2 Dif Intel","Gen1 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Joint_Intelligence_Dif_Child_AFI_11.tex"))

@@

\subsubsection{Intelligence} Cousin differences in intelligence as assessed at ages 9.5, 10.5, and 11.5 were correlated using three different linking methods (Mixed, Daughters, Sons). Reliabilities across linking methods was consistent and high (min r = .86; max r = .95). However, we could not estimate test-retest reliabilities for Generation 1; we calculated the reliability using Lord's (\citeyear{Lord1963}) equation. The calculated reliability of Generation 1's differences in AFQT was \Sexpr{r.diff.intelligence}0, which was marginally acceptable, and obviously lower than the empirical correlation we derived for cousin differences.%\Sexpr{r.diff.intelligence}

%%%%%%%%%%%% Results %%%%%%%%%%%%
\section{Results}
\input{../Common/content/writing/results.tex}
%
% Between-Family
\subsection{Between-Family Analyses}
\input{../Common/content/writing/results_between.tex}

@@

%%%%%%%%%%%% Discussion %%%%%%%%%%%%
\section{Discussion}
\input{../Common/content/writing/discussion.tex}
%%%%%%%%%%%% References %%%%%%%%%%%%
\bibliography{Projects-AFI}
%%%%%%%%%%%% Appendix %%%%%%%%%%%%
   \begin{landscape} \appendix\label{appen}
  %
  % Age 10.5 Replication
  \section{Age 10.5 Replication}\label{appen10}
  %% Between-Family

@@

\end{document}

>>>>

\documentclass[a4paper,man,apacite,natbib,12pt,longtable,mask]{apa6}
\usepackage{../Common/style/Mason}
\usepackage{listings}
\usepackage{inconsolata}
\usepackage[bottom]{footmisc} %fix footnotes
\usepackage{lineno}
\usepackage{adjustbox}
\def\hyph{-\penalty0\hskip0pt\relax}  % trick hyphen
%\linenumbers
\interfootnotelinepenalty=10000
%%%%%%%%%%%% Title %%%%%%%%%%%%
\title{Casting doubt on the causal link between intelligence and age at first intercourse:\\ A cross-generational sibling comparison design using the NLSY}
\shorttitle{Intelligence and AFI}
%
% Authors and Affiliations
\author{S. Mason Garrison and Joseph Lee Rodgers}
\affiliation{Vanderbilt University}
%
% Author Note
\authornote{\input{../Common/content/title/authornote.tex}}
%
% Abstract
\abstract{%Last compiled \today\ at \currenttime\\
\input{../Common/content/title/abstract_empreport.txt}}
%
% Key Words
\keywords{Age at first intercourse; Cross-sectional Data; Discordant Sibling Design; Intelligence; Quasi-Experimental; Siblings}
%
\begin{document}
\maketitle

@@

  listing <- function(x, options){
    paste("\\begin{lstlisting}[style=Rsettings]\n",
      x, "\\end{lstlisting}\n", sep = "")}
  knit_hooks$set(source=listing, output=listing)
@
<<setup, include=FALSE>>=
# Libraries
## Install Most Current Version
library(devtools)#;dev_mode(on=T)
#install_github("LiveOak/NlsyLinks")
#install_github("harrelfe/Hmisc");dev_mode(on=F)
## Attach Remaining
library(corrplot)
library(ggplot2);library(ggExtra);library(gtable)
library(grid);library(gridExtra)
library(Hmisc)
library(MplusAutomation)
library(NlsyLinks)
library(plyr);library(psych);library(ppcor)
library(QuantPsyc)
#library(stargazer)
library(tables)
library(xtable)

@@

#### Age 11
capture.output(stargazer(ModelSummaries_Mplusg2_11,summary=FALSE,flip = TRUE, dep.var.labels.include = FALSE),file=paste0(directory,"/Common/content/tables/table_g2_11measurement.tex"))
capture.output(stargazer(g2loading_11,summary=FALSE,flip = FALSE, dep.var.labels.include = FALSE),file=paste0(directory,"/Common/content/tables/table_g2loading_11.tex"))
@
<<results_regression,echo=FALSE, comment=NA, include=FALSE,cache=TRUE>>=
# Stargazer Plot defaults
font.size="small"
no.space=TRUE
style="demography"
column.sep.width = "1pt"
header = FALSE
column.labels = c("Mixed", "Daughters", "Sons")
model.numbers=FALSE
float=FALSE
ci =TRUE
single.row = TRUE
notes.append = TRUE
digit = 2
digits.extra=1
# 9.5
capture.output(stargazer(model.meanmoms_9,model.meanmoms.g_9,model.meanmoms.b_9,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Mom_Intelligence_Mean_Child_AFI_9.tex"))

capture.output(stargazer(model.meankids_9,model.meankids.g_9,model.meankids.b_9,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Child_Intelligence_Mean_Child_AFI_9.tex"))

capture.output(stargazer(model.meanmomskids_9,model.meanmomskids.g_9,model.meanmomskids.b_9,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel","Gen2 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Joint_Intelligence_Mean_Child_AFI_9.tex"))

capture.output(stargazer(model.diffmoms_9,model.diffmoms.g_9,model.diffmoms.b_9,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen1 Mean Intel", "Gen1 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Mom_Intelligence_Dif_Child_AFI_9.tex"))

capture.output(stargazer(model.diffkids_9,model.diffkids.g_9,model.diffkids.b_9,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen2 Mean Intel", "Gen2 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Child_Intelligence_Dif_Child_AFI_9.tex"))

capture.output(stargazer(model.diffmomskids_9,model.diffmomskids.g_9,model.diffmomskids.b_9,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen2 Mean Intel","Gen1 Mean Intel","Gen2 Dif Intel","Gen1 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Joint_Intelligence_Dif_Child_AFI_9.tex"))

# 10.5
capture.output(stargazer(model.meanmoms_10,model.meanmoms.g_10,model.meanmoms.b_10,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Mom_Intelligence_Mean_Child_AFI_10.tex"))

capture.output(stargazer(model.meankids_10,model.meankids.g_10,model.meankids.b_10,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Child_Intelligence_Mean_Child_AFI_10.tex"))

capture.output(stargazer(model.meanmomskids_10,model.meanmomskids.g_10,model.meanmomskids.b_10,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel","Gen2 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Joint_Intelligence_Mean_Child_AFI_10.tex"))

capture.output(stargazer(model.diffmoms_10,model.diffmoms.g_10,model.diffmoms.b_10,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen1 Mean Intel", "Gen1 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Mom_Intelligence_Dif_Child_AFI_10.tex"))

capture.output(stargazer(model.diffkids_10,model.diffkids.g_10,model.diffkids.b_10,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen2 Mean Intel", "Gen2 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Child_Intelligence_Dif_Child_AFI_10.tex"))

capture.output(stargazer(model.diffmomskids_10,model.diffmomskids.g_10,model.diffmomskids.b_10,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen2 Mean Intel","Gen1 Mean Intel","Gen2 Dif Intel","Gen1 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Joint_Intelligence_Dif_Child_AFI_10.tex"))

# 11.5
capture.output(stargazer(model.meanmoms_11,model.meanmoms.g_11,model.meanmoms.b_11,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Mom_Intelligence_Mean_Child_AFI_11.tex"))

capture.output(stargazer(model.meankids_11,model.meankids.g_11,model.meankids.b_11,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Child_Intelligence_Mean_Child_AFI_11.tex"))

capture.output(stargazer(model.meanmomskids_11,model.meanmomskids.g_11,model.meanmomskids.b_11,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel","Gen2 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Joint_Intelligence_Mean_Child_AFI_11.tex"))

capture.output(stargazer(model.diffmoms_11,model.diffmoms.g_11,model.diffmoms.b_11,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen1 Mean Intel", "Gen1 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Mom_Intelligence_Dif_Child_AFI_11.tex"))

capture.output(stargazer(model.diffkids_11,model.diffkids.g_11,model.diffkids.b_11,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen2 Mean Intel", "Gen2 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Child_Intelligence_Dif_Child_AFI_11.tex"))

capture.output(stargazer(model.diffmomskids_11,model.diffmomskids.g_11,model.diffmomskids.b_11,
                         font.size=font.size,
                         no.space=no.space,
						 digits=digit,
						 digits.extra=digits.extra,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen2 Mean AFI","Gen2 Mean Intel","Gen1 Mean Intel","Gen2 Dif Intel","Gen1 Dif Intel"),
                         dep.var.labels=c("Gen2 Differences in AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Dif_Joint_Intelligence_Dif_Child_AFI_11.tex"))

@@

\subsubsection{Intelligence} Cousin differences in intelligence as assessed at ages 9.5, 10.5, and 11.5 were correlated using three different linking methods (Mixed, Daughters, Sons). Reliabilities across linking methods was consistent and high (min r = .86; max r = .95). However, we could not estimate test-retest reliabilities for Generation 1; we calculated the reliability using Lord's (\citeyear{Lord1963}) equation. The calculated reliability of Generation 1's differences in AFQT was \Sexpr{r.diff.intelligence}0, which was marginally acceptable, and obviously lower than the empirical correlation we derived for cousin differences.%\Sexpr{r.diff.intelligence}
%\vspace{-.2cm}
%%%%%%%%%%%% Results %%%%%%%%%%%%
\section{Results}
%\vspace{-.2cm}
\input{../Common/content/writing/results.tex}
%
% Between-Family
%\vspace{-.2cm}
\subsection{Between-Family Analyses}
%\vspace{-.2cm}
\input{../Common/content/writing/results_between.tex}

@@

%%%%%%%%%%%% Discussion %%%%%%%%%%%%
\section{Discussion}
\input{../Common/content/writing/discussion.tex}
%%%%%%%%%%%% References %%%%%%%%%%%%
\bibliography{Projects-AFI}
%%%%%%%%%%%% Appendix %%%%%%%%%%%%
\appendix\label{appen}
\begin{landscape} 
  % Age 10.5 Replication
  \section{Age 10.5 Replication}\label{appen10}
  %% Between-Family

@@

  \section{Correlations}\label{appencor}  
\noindent
\captionof{table}{Zero-Order Correlations}\label{table_cor}
\begin{center}
<<reviewer2_cor,fig=TRUE,cache=TRUE,echo=FALSE,warning=FALSE, fig.height=10, fig.width=10,out.width="1\\textwidth">>=
LinkedMDAN_z_9_cor<-LinkedMDAN_discord_AFI_z_9[,c(66,67,70,71,89,90)]
LinkedMDAN_b_9_cor<-LinkedMDAN_discord_AFI_b_9[,c(67,68,71,72,75,92)]
LinkedMDAN_g_9_cor<-LinkedMDAN_discord_AFI_g_9[,c(67,68,71,72,74,92)]
col1 <- colorRampPalette(c("#7F0000","red","#FF7F00","yellow","black","cyan", "#007FFF", "blue","#00007F"))
names(LinkedMDAN_z_9_cor)<-c("G1 Dif Intel","G1 Mean Intel","G2 Dif AFI","G2 Mean AFI","G2 Mean Intel","G2 Dif Intel")
names(LinkedMDAN_b_9_cor)<-c("G1 Dif Intel","G1 Mean Intel","G2 Dif AFI","G2 Mean AFI","G2 Mean Intel","G2 Dif Intel")
names(LinkedMDAN_g_9_cor)<-c("G1 Dif Intel","G1 Mean Intel","G2 Dif AFI","G2 Mean AFI","G2 Mean Intel","G2 Dif Intel")
M <- cor(LinkedMDAN_z_9_cor,use = "pairwise.complete.obs")
corrplot(M, method="number",type="lower",tl.cex = 1,tl.pos="ld", tl.srt=60,number.font=.5,number.cex = 2,number.digits=2,tl.col = 'black',col=col1(5),order="alphabet")
\end{center}\pagebreak

\noindent\begin{minipage}{\textwidth}
<<reviewer2_spcor_btw,echo=FALSE,warning=FALSE>>=
library(ppcor)
#mixed
LinkedMDAN_cor_btw<-LinkedMDAN_z_9_cor[c(2,4,5)]
LinkedMDAN_cor_btw<-as.matrix(LinkedMDAN_cor_btw[complete.cases(LinkedMDAN_cor_btw),])
LinkedMDAN_cor_wtn<-as.matrix(LinkedMDAN_z_9_cor[complete.cases(LinkedMDAN_z_9_cor),])

##between
spcor_z_9_cor_g1meang_btw<-spcor.test(y=LinkedMDAN_cor_btw[,2],x=LinkedMDAN_cor_btw[,1],z=LinkedMDAN_cor_btw[,3],method = "pearson")
spcor_z_9_cor_g2meang_btw<-spcor.test(y=LinkedMDAN_cor_btw[,2],x=LinkedMDAN_cor_btw[,3],z=LinkedMDAN_cor_btw[,1],method = "pearson")
